---
title: "ACST886 Assignment3Q2"
author: "Chang,Liu"
date: "02/10/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part a

### Generate multiple decrement table
```{r}
x<-c(30:40)
qx_d_ind<-c(0.00043,0.00042,0.00041,0.0004,0.00041,0.00042,0.00043,0.00045,0.00049,0.00053,NA)
qx_w_ind<-c(0.250,0.200,0.175,0.150,0.150,0.150,0.150,0.150,0.150,1.000,NA)
qx.d.dep<-c()
qx.w.dep<-c()
for (j in 1:11) {
  qx.d.dep[j]<-qx_d_ind[j]*(1-0.5*qx_w_ind[j])
  qx.w.dep[j]<-qx_w_ind[j]*(1-0.5*qx_d_ind[j])
  }
al.x <- c()
ad.x <- c()
ad.w <- c()
al.x[1]<-100000
for (j in 1:10) {
  ad.x[j]<-al.x[j]*qx.d.dep[j]
  ad.w[j]<-al.x[j]*qx.w.dep[j]
  al.x[j+1]<-al.x[j]-ad.x[j]-ad.w[j]
}
ad.w[11]<-NA
ad.x[11]<-NA
junk<-cbind(x,qx_d_ind,qx_w_ind,qx.d.dep,qx.w.dep,al.x,ad.x,ad.w)
colnames(junk)<-c("age","qx_d_ind","qx_w_ind","qx.d.dep","qx.w.dep","al.x","ad.x","ad.w")
junk
```

### Unit fund
```{r}
Premium<-5000
i_unit<-0.1
Pbase<-c(0.45,rep(0.01,9))
Asset<-0.003
BSmargin<-0.005
invsetPre<-c()
Exp_invsetPre<-c()
Exp_interest<-c()
Value_unit<-c()
for (j in 1:10) {
  invsetPre[j]<-Premium*(1-Pbase[j])*(1-BSmargin)
  Exp_invsetPre[j]<- invsetPre[j]*(al.x[j]/al.x[1])
  }
Exp_interest[1]<-Exp_invsetPre[1]*i_unit
Value_unit[1]<-invsetPre[1]*(1+i_unit)*(1-Asset)
Exp_unitvalue<-c()
Exp_unitvalue[1]<-Value_unit[1]*(al.x[2]/al.x[1])
for (j in 2:10) {
  Value_unit[j]<-(invsetPre[j]+Value_unit[j-1])*(1+i_unit)*(1-Asset)
  Exp_unitvalue[j]<-Value_unit[j]*(al.x[j+1]/al.x[1])
  Exp_interest[j]<-(Exp_invsetPre[j]+Exp_unitvalue[j-1])*i_unit
}
Trans2non_unit<-c()
Trans2non_unit[1]<-Exp_invsetPre[1]+Exp_interest[1]-Exp_unitvalue[1]
for (j in 2:10) {
  Trans2non_unit[j]<-Exp_invsetPre[j]+Exp_interest[j]+Exp_unitvalue[j-1]-Exp_unitvalue[j]
}
Trans2non_unit
```

### Non-unit fund
```{r}
Init_expense<-0.45
maint_expense<-58
i_f<-0.2
i_nonunit<-0.08
Pbasefee<-c()
BSmarfee<-c()
Expense<-c()
Bft<-Value_unit
Exp_Pbasefee<-c()
Exp_BSmarfee<-c()
Exp_Expense<-c()
Exp_interest2<-c()
S_bft<-c()
D_bft<-c()
Trans<-c()
Pbasefee<-Premium*Pbase
BSmarfee<-Premium*(1-Pbase)*BSmargin
Expense[1]<-Init_expense*Premium+maint_expense
  for (j in 2:10) {
    Expense[j]<-maint_expense*(1+i_f)^(j-1)
  }

for (j in 1:10) {
  Exp_Pbasefee[j]<-Pbasefee[j]*(al.x[j]/al.x[1])
  Exp_BSmarfee[j]<-BSmarfee[j]*(al.x[j]/al.x[1])
  Exp_Expense[j]<-Expense[j]*(al.x[j]/al.x[1])
  Exp_interest2[j]<-(Exp_Pbasefee[j]+Exp_BSmarfee[j]-Exp_Expense[j])*i_nonunit
  D_bft[j]<-Bft[j]*(ad.x[j]/al.x[1])
  S_bft[j]<-Bft[j]*(ad.w[j]/al.x[1])
}
Trans<-Exp_Pbasefee+Exp_BSmarfee-Exp_Expense+Exp_interest2+Trans2non_unit-D_bft-S_bft
Trans
```

### profit signature and the expected present value of transfer at 12.5% p.a
```{r}
i_risk<-0.125
prof.sig<-Trans
prof.sig
  disc.fact<-c()
for (j in 1:10) {
  disc.fact[j]<-(1+i_risk)^(-j)
  
}
Exp.PV<-sum(prof.sig*disc.fact)
Exp.PV
```

## Part b

```{r}
policy_val<-Value_unit
f<-function(x){
  Value_unit[9]<-x
  for (j in 9:10) {
  Exp_unitvalue[j]<-Value_unit[j]*(al.x[j+1]/al.x[1])
  Exp_interest[j]<-(Exp_invsetPre[j]+Exp_unitvalue[j-1])*i_unit
}
  for (j in 9:10) {
  Trans2non_unit[j]<-Exp_invsetPre[j]+Exp_interest[j]+Exp_unitvalue[j-1]-Exp_unitvalue[j]
}
  
Trans<-Exp_Pbasefee+Exp_BSmarfee-Exp_Expense+Exp_interest2+Trans2non_unit-D_bft-S_bft  
Trans[10]  
}
y<-seq(0.001,1,0.001)
transfer_10<-c()
for (j in 1:1000) {
  a<-y[j]
  transfer_10[j]<-f(a)
}
plot(y,transfer_10,type="l",xlab="policy value in year 9",ylab="transfer in final year")
```
We can see from the plot that the policy value required is between 66000 and 68000, then we use uniroot function to determine the exact value
```{r}
abc<-uniroot(f,c(66000,68000))
abc$root
```

## Part c
```{r}
Value_unit[9]<-67319.02
 for (j in 9:10) {
  Exp_unitvalue[j]<-Value_unit[j]*(al.x[j+1]/al.x[1])
  Exp_interest[j]<-(Exp_invsetPre[j]+Exp_unitvalue[j-1])*i_unit
}
  for (j in 9:10) {
  Trans2non_unit[j]<-Exp_invsetPre[j]+Exp_interest[j]+Exp_unitvalue[j-1]-Exp_unitvalue[j]
}
  
Trans<-Exp_Pbasefee+Exp_BSmarfee-Exp_Expense+Exp_interest2+Trans2non_unit-D_bft-S_bft  
Exp.PV2<-sum(Trans*disc.fact)
Exp.PV2
Exp.PV-Exp.PV2
```

the expected present value of transfer at 12.5% p.a. decreased as a result of the zeroisation,
because the transfer to non-unit fund is decreased as a result of the samller difference between the policy value in year 8 and that in year 9