---
title: "ACST886 Assignment3Q1"
author: "Chang,Liu"
date: "01/10/2019"
output: word_document
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1(a)

### (i)

```{r}
x <- c(55:58)
x
```

#### life table

```{r}
qx_d <- c(0.001046,0.001199,0.001375,NA)
l_x<-c()
l_x[1]=100000
for (j in 2:4) {
  l_x[j]=l_x[j-1]*(1-qx_d[j-1])
}
junk<-cbind(x,qx_d,l_x)
colnames(junk)<-c("age","qx_d","l_x")
junk
```

#### Premium
In this question we only have one Premium which is the purchase price at beginning of the first year
```{r}
Premium<-40250
Premium
```

#### Expense 
In this question the expense including annities, initial expenses and payment expenses.
```{r}
annuity<-15000
annuity_paid<-c(15000,15000*(1+0.0192308),15000*(1+0.0192308)^2)
init_expense<-40250*0.015+100
maint_expense<-c(10,10*(1+0.05),10*(1+0.05)^2)
E.maint_expense<-c()
Exp.annuity<-c()
for (j in 1:3) {
  E.maint_expense[j]<-maint_expense[j]*(l_x[j+1]/l_x[1])
  
  Exp.annuity[j]<-annuity_paid[j]*(l_x[j+1]/l_x[1])
}
E.maint_expense
Exp.annuity
```
#### Policy value

```{r warning=FALSE}
A57t2<-0.924607
A56t3<-0.889132
i_vb<-0.04
pol_val<-c()
Exppol_val<-c()
v<-(1+i_vb)^(-1)
d<-1-(1+i_vb)^(-1)
a_1<-(v-A56t3)/d
a_2<-(v-A57t2)/d
pol_val[1]<-annuity*a_1
pol_val[2]<-annuity_paid[2]*a_2
pol_val[3]<-0
for (j in 1:3) {
  Exppol_val[j]<-pol_val[j]*l_x[j+1]/l_x[1]
  
}

pol_val
Exppol_val
```
#### Interest earned
 
```{r}
i<-0.08
Exp_Int<-c()
Exp_Int[1]<-(Premium-init_expense[1])*i
for (j in 2:3) {
  Exp_Int[j]<-Exppol_val[j-1]*i
}

Exp_Int
```
#### Profit signature

```{r}
Pro.sig<-c()
Pro.sig[1]<-Premium-init_expense+Exp_Int[1]-Exppol_val[1]-E.maint_expense[1]-Exp.annuity[1]
for (j in 2:3) {
  Pro.sig[j]<-Exp_Int[j]-Exppol_val[j]+Exppol_val[j-1]-E.maint_expense[j]-Exp.annuity[j]
}
 Pro.sig
```

### (ii)

#### Net expected profit
```{r}
disc.fact<-c()
risk_disc<-0.12
for (j in 1:3) {
  disc.fact[j]<-(1+risk_disc)^(-(j-1))
                    
}
Exp.profit<-sum(Pro.sig*disc.fact)
Exp.profit
```
#### Profit margin
```{r}
Pro_margin<-Exp.profit/40250
Pro_margin
```

## Question 1(b)
```{r}
f<-function(i){
for (j in 1:3) {
  disc.fact[j]<-(1+i)^(-(j-1))
                    
}
  sum(Pro.sig*disc.fact)
}
i<-seq(0.01,1,0.01)
npv<-c()

for (j in 1:length(i)) {
  a<-i[j]
  npv[j]<-f(a)
}
plot(i,npv,type="l",xlab="interest rate",ylab="Net Present Value")
```

```{r}
acd<-uniroot(f,c(0.2,0.8))
acd$root
```
The reason is that from the graph we can see that the net present vale decreses as the interest rate increase.And the first cashflow has the biggest influence since we need to time it by v^(-1),while following one need to time smaller discount factor,thus we need a big interest rate to increase the influence.